### 2020-01-19 Temp_tables/summaryStatistics.tex
intend tables
update latex table

\begin{table}[!htbp] \centering 
    %\resizebox{1\textwidth}{!}{
    \begin{threeparttable} 
    \caption{\small Summary of TCZ results over time}
        \begin{tabular}{lrrrr}
        \toprule
            {} & \multicolumn{2}{l}{Failure} & \multicolumn{1}{l}{Success} \\
            \hline
             &      (1998-2000) & (2001-2005) &  (2006-2010) \\
            \midrule
            \textbf{TCZ} & & & \\
                \text{\footnotesize{SO2 target}} &-& -& -14\%& \\
                \text{\footnotesize{SO2 \% reduction}} & -31\%&26\% &X & \\

            \textbf{No TCZ} & & & \\
                \text{\footnotesize{SO2 target}} & -& -& -4\%& \\
                \text{\footnotesize{SO2 \% reduction}} & 34\% & 43\% &X & \\

            \textbf{All sample} & & & \\
                \text{\footnotesize{SO2 target}} & -& -10\%& -10\%& \\
                \text{\footnotesize{SO2 \% reduction}} & X& 34\%& -14\%& \\

        \bottomrule
        \end{tabular}
        \begin{tablenotes}
                \small
            \item The TCZ policy is evaluated at 2 points in time, 2000 and 2010. In 2005, the chinese governement, facing a poor environmental achievement, decided to reinforce the environmental policy for the TCZ. The TCZ and the 11th FYP have now joint results, say differently, each TCZ city have a clear environmental objective. When both 11th FYP and TCZ have joint objectives, the environmental policy is a success. Prior years demonstrate a failure\\
            Sources: Author's own computation 
        \end{tablenotes}
    \end{threeparttable}
    %}
\end{table}

@@

\begin{table}[!htbp] \centering 
    %\resizebox{1\textwidth}{!}{
        \begin{threeparttable}  
            \caption{\small Summary Statistics by City-industry characteristics and City characteristics}
            \begin{tabular}{lrrrr}
            \multicolumn{1}{l}{\textbf{Panel A: City characteristics}} \\
            \toprule
                & \multicolumn{2}{l}{No TCZ} & \multicolumn{2}{l}{TCZ} \\
                {} &       mean &        std &       mean &        std \\
            \midrule
                SO2_{cit}                    & 182873 & 372028 & 174308 & 357225 \\
                \text{count share SOE}_i   &      0.093 &      0.094 &      0.082 &      0.086 \\
                \text{output share SOE}_i  &      0.147 &      0.153 &      0.136 &      0.151 \\
                \text{capital share SOE}_i &      0.220 &      0.197 &      0.209 &      0.198 \\
                \text{labour share SOE}_i  &      0.188 &      0.162 &      0.176 &      0.162 \\
                \text{output}_{cit}          &      0.028 &      0.101 &      0.058 &      0.266 \\
                \text{capital}_{cit}         &      0.008 &      0.030 &      0.014 &      0.054 \\
                \text{labour}_{cit}          &      0.009 &      0.024 &      0.016 &      0.056 \\
            \bottomrule
            \\ %%% Create second table
            \multicolumn{1}{l}{\textbf{Panel B: Count number of cities}} \\
            \toprule
                {} &  No TCZ & & TCZ & Total \\
                Full Sample     &      88 & &  140 &    228 \\
                SPZ     &      11 & &   48 &     59 \\
                Coastal &      27 & &   68 &     95 \\
            \hline
            \end{tabular}
            \begin{tablenotes}
                \small
                \item Panel A provides a summary statistics for the variables that vary by city-industry-year. Panel B counts the number of cities by TCZ and non TCZ. For instance, the full sample gathers 88 TCZ cities and 140 non TCZ cities. Among the 80 TCZ cities, 11 are also SPZ and 27 are located in the coastal areas. \\
                Sources: Author's own computation 
            \end{tablenotes}

\end{threeparttable}
%}
\end{table}

\begin{table}[!htbp] \centering 
    %\resizebox{1\textwidth}{!}{
    \begin{threeparttable} 
    \caption{\small Summary Statistics of the SO2 emission by City-location}
        \begin{tabular}{lrrrr}
        \toprule
            {} & \multicolumn{2}{l}{difference} & \multicolumn{2}{l}{variance} \\
             &      No TCZ &         TCZ &   No TCZ &  TCZ \\
            Location    &             &             &          &      \\
            \midrule
            Full sample & -1919200 & -4360643 &     0.22 & 0.26 \\
            Central     & -2381649 & -2318221 &     0.25 & 0.19 \\
            Coastal     & -1376522 & -6590904 &     0.12 & 0.29 \\
            Northeast   & -2060869 &  -893667 &     0.30 & 0.08 \\
            Northwest   & -1148382 & -2772765 &     0.21 & 0.31 \\
            Southwest   & -2717954 & -5025523 &     0.31 & 0.29 \\
            Non Coastal & -2147154 & -3015876 &     0.28 & 0.23 \\
            Coastal     & -1404192 & -5784514 &     0.13 & 0.28 \\
        \bottomrule
        \end{tabular}
        \begin{tablenotes}
                \small
            \item Difference (variance) of the average SO2 emission before and after the introduction of the 11th FYP by TCZ and No TCZ. More precisely, we sum the SO2 emission by city for the period before 2005 and after 2005, then we computed the average across city. Next, we computed the difference between TCZ and No TCZ. First row shows that TCZ cities reduced the SO2 emission by 26\% while No TCZ by 22\% \\
            Sources: Author's own computation 
        \end{tablenotes}
    \end{threeparttable}
    %}
\end{table} 
\end{document}

>>>>

\begin{table}[!htbp] \centering
  \caption{Summary of TCZ results over time}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{lrrrr}
      \toprule
      {} & \multicolumn{2}{l}{Failure} & \multicolumn{1}{l}{Success} \\
      \hline
      &      (1998-2000) & (2001-2005) &  (2006-2010) \\
      \midrule
      \textbf{TCZ} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -     & -14\% &   \\
      \text{\footnotesize{SO2 \% reduction}} & -7\% & 38\%  & X     &   \\

      \textbf{No TCZ} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -     & -4\%  &   \\
      \text{\footnotesize{SO2 \% reduction}} & 21\%  & 64\%  & X     &   \\

      \textbf{All sample} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -10\% & -10\% &   \\
      \text{\footnotesize{SO2 \% reduction}} & -2\%     & 45\%  & -14\% &   \\

      \bottomrule
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item The TCZ policy is evaluated at 2 points in time, 2000 and 2010. In 2005, the chinese governement, facing a poor environmental achievement, decided to reinforce the environmental policy for the TCZ. The TCZ and the 11th FYP have now joint results, say differently, each TCZ city have a clear environmental objective. When both 11th FYP and TCZ have joint objectives, the environmental policy is a success. Prior years demonstrate a failure\\
      Sources: Author's own computation
    \end{tablenotes}
\end{table}

@@

\begin{table}[!htbp] \centering
    \caption{ Summary Statistics by city-industry and city characteristics}
      \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{lrrrr}
      \multicolumn{1}{l}{\textbf{\small Panel A: City/city-industry}} \\
      \toprule
      & \multicolumn{2}{l}{No TCZ} & \multicolumn{2}{l}{TCZ} \\
      {}                         & mean   & std    & mean   & std    \\
      \midrule
      SO2_{ikt}                  & 182873 & 372028 & 174308 & 357225 \\
      \text{count share SOE}_k   & 0.093  & 0.094  & 0.082  & 0.086  \\
      \text{output share SOE}_k  & 0.147  & 0.153  & 0.136  & 0.151  \\
      \text{capital share SOE}_k & 0.220  & 0.197  & 0.209  & 0.198  \\
      \text{labour share SOE}_k  & 0.188  & 0.162  & 0.176  & 0.162  \\
      \text{output}_{kit}        & 0.028  & 0.101  & 0.058  & 0.266  \\
      \text{capital}_{kit}       & 0.008  & 0.030  & 0.014  & 0.054  \\
      \text{labour}_{kit}        & 0.009  & 0.024  & 0.016  & 0.056  \\
      \bottomrule
      \\ %%% Create second table
      \multicolumn{1}{l}{\textbf{\small Panel B: SO2 emission by city-location}} \\
      \toprule
      {} & \multicolumn{2}{l}{\footnotesize difference (10.000 tons units)} & \multicolumn{2}{l}{variance (\footnotesize \%)} \\
                  & No TCZ   & TCZ      & No TCZ & TCZ  \\
      Location    &          &          &        &      \\
      \midrule
      Full sample &    -192 & -436 &     0.22 & 0.26 \\
      Central     &    -238 & -232 &     0.25 & 0.19 \\
      Coastal     &    -138 & -659 &     0.12 & 0.29 \\
      Northeast   &    -206 &  -89 &     0.30 & 0.08 \\
      Northwest   &    -115 & -277 &     0.21 & 0.31 \\
      Southwest   &    -272 & -503 &     0.31 & 0.29 \\
      Non Coastal &    -215 & -302 &     0.28 & 0.23 \\
      Coastal     &    -140 & -578 &     0.13 & 0.28 \\
      \bottomrule
      \hline
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item Panel A provides summary statistics for the main variables used in the subsequent empirical analysis. 
       \\
      Panel B provides Difference (variance) of the average SO2 emission (in 10.000 tons unit) before and after the introduction of the 11th FYP by TCZ and No TCZ. More precisely, we sum the SO2 emission by city for the period before 2005 and after 2005, then we computed the average across city. Next, we computed the difference between TCZ and No TCZ. First row shows that TCZ cities reduced the SO2 emission by 26\% while No TCZ by 22\% during the second period compared with the first period
      \\
      Sources: Author's own computation
    \end{tablenotes}
\end{table}
\end{document}

### 2020-01-19 Temp_tables/table_3.tex
update latex table

      & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i                                         & $-$0.275$^{*}$ & $-$0.320$^{**}$ & $-$0.331$^{**}$ & $-$0.378$^{**}$ \\

@@

      SPZ_c \times \text{Period} \times \text{Polluted}_i                                         & 0.081          & 0.070           & 0.004           & 0.019           \\

@@

      Coastal_c \times \text{Period} \times \text{Polluted}_i                                     & $-$0.083       & $-$0.034        & $-$0.034        & $-$0.044        \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}       & 1.531          &                 &                 &                 \\

@@

      SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}       & 0.181          &                 &                 &                 \\

@@

      Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}   & 0.077          &                 &                 &                 \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}      &                & 1.305$^{*}$     &                 &                 \\

@@

      SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}      &                & 0.300           &                 &                 \\

@@

      Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  &                & $-$0.327        &                 &                 \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}     &                &                 & 0.924           &                 \\

@@

      SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}     &                &                 & 0.477           &                 \\

@@

      Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i} &                &                 & $-$0.150        &                 \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}      &                &                 &                 & 1.391$^{*}$     \\

@@

      SPZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}      &                &                 &                 & 0.525           \\

@@

      Coastal_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &                &                 &                 & $-$0.142        \\

@@

      \textit{Note:}  & \multicolumn{4}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
      & \multicolumn{4}{l}{Heteroskedasticity-robust standard errors in parentheses} \\
      & \multicolumn{4}{l}{are clustered by city} \\

@@

>>>>

      & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{ikt}} \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k                                         & $-$0.275$^{*}$ & $-$0.320$^{**}$ & $-$0.331$^{**}$ & $-$0.378$^{**}$ \\

@@

      SPZ_i \times \text{Period} \times \text{Polluted}_k                                         & 0.081          & 0.070           & 0.004           & 0.019           \\

@@

      Coastal_i \times \text{Period} \times \text{Polluted}_k                                     & $-$0.083       & $-$0.034        & $-$0.034        & $-$0.044        \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{count share SOE}_{k}       & 1.531          &                 &                 &                 \\

@@

      SPZ_i \times \text{Period} \times \text{Polluted}_k \times \text{count share SOE}_{k}       & 0.181          &                 &                 &                 \\

@@

      Coastal_i \times \text{Period} \times \text{Polluted}_k \times \text{count share SOE}_{k}   & 0.077          &                 &                 &                 \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{output share SOE}_{k}      &                & 1.305$^{*}$     &                 &                 \\

@@

      SPZ_i \times \text{Period} \times \text{Polluted}_k \times \text{output share SOE}_{k}      &                & 0.300           &                 &                 \\

@@

      Coastal_i \times \text{Period} \times \text{Polluted}_k \times \text{output share SOE}_{k}  &                & $-$0.327        &                 &                 \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{capital share SOE}_{k}     &                &                 & 0.924           &                 \\

@@

      SPZ_i \times \text{Period} \times \text{Polluted}_k \times \text{capital share SOE}_{k}     &                &                 & 0.477           &                 \\

@@

      Coastal_i \times \text{Period} \times \text{Polluted}_k \times \text{capital share SOE}_{k} &                &                 & $-$0.150        &                 \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{labour share SOE}_{k}      &                &                 &                 & 1.391$^{*}$     \\

@@

      SPZ_i \times \text{Period} \times \text{Polluted}_k \times \text{labour share SOE}_{k}      &                &                 &                 & 0.525           \\

@@

      Coastal_i \times \text{Period} \times \text{Polluted}_k \times \text{labour share SOE}_{k}  &                &                 &                 & $-$0.142        \\

@@

@@

  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}

### 2020-01-19 Temp_tables/table_4.tex
update latex table

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Dec 08, 2019 - 08:55:57

@@

      \text{Polluted}_i \times \text{ln gdp per cap)}_{ct}                                    & $-$0.038 & $-$0.034        & $-$0.029        & $-$0.036        \\

@@

      \text{Polluted}_i \times \text{ln population)}_{ct}                                     & 0.165    & 0.170           & 0.172           & 0.172           \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i                                     & $-$0.238 & $-$0.280$^{**}$ & $-$0.317$^{**}$ & $-$0.360$^{**}$ \\

@@

      TCZ_c \times \text{Period} \times \text{count share SOE}_{i}                            & $-$1.177 &                 &                 &                 \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{count share SOE}_{i}   & 1.522    &                 &                 &                 \\

@@

      TCZ_c \times \text{Period} \times \text{output share SOE}_{i}                           &          & $-$0.842        &                 &                 \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  &          & 1.327$^{*}$     &                 &                 \\

@@

      TCZ_c \times \text{Period} \times \text{capital share SOE}_{i}                          &          &                 & $-$0.707        &                 \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i} &          &                 & 1.074$^{*}$     &                 \\

@@

      TCZ_c \times \text{Period} \times \text{labour share SOE}_{i}                           &          &                 &                 & $-$1.044$^{*}$  \\

@@

      TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &          &                 &                 & 1.545$^{**}$    \\

>>>>

@@

      \text{Polluted}_k \times \text{ln gdp per cap}_{it}                                    & $-$0.038 & $-$0.034        & $-$0.029        & $-$0.036        \\

@@

      \text{Polluted}_k \times \text{ln population}_{it}                                     & 0.165    & 0.170           & 0.172           & 0.172           \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k                                     & $-$0.238 & $-$0.280$^{**}$ & $-$0.317$^{**}$ & $-$0.360$^{**}$ \\

@@

      TCZ_i \times \text{Period} \times \text{count share SOE}_{k}                            & $-$1.177 &                 &                 &                 \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{count share SOE}_{k}   & 1.522    &                 &                 &                 \\

@@

      TCZ_i \times \text{Period} \times \text{output share SOE}_{k}                           &          & $-$0.842        &                 &                 \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{output share SOE}_{k}  &          & 1.327$^{*}$     &                 &                 \\

@@

      TCZ_i \times \text{Period} \times \text{capital share SOE}_{k}                          &          &                 & $-$0.707        &                 \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{capital share SOE}_{k} &          &                 & 1.074$^{*}$     &                 \\

@@

      TCZ_i \times \text{Period} \times \text{labour share SOE}_{k}                           &          &                 &                 & $-$1.044$^{*}$  \\

@@

      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{labour share SOE}_{k}  &          &                 &                 & 1.545$^{**}$    \\

### 2020-01-19 Temp_tables/table_6.tex
update latex table

\begin{table}[htbp]\centering
  \resizebox{1\textwidth}{!}{
    \begin{threeparttable}
      \caption{\small Summary Statistics by City-industry characteristics and City characteristics}
      \begin{tabular}{lrrrr}
        \multicolumn{1}{l}{\textbf{Panel A: SOE dominated sector}} \\
        \toprule
        & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\
        \cline{2-5}
        \\[-1.8ex] & (1) & (2) & (3) & (4)\\
        \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
        \hline \\[-1.8ex]
        TCZ_c \times \text{Polluted}_i \times \text{Period} & $-$0.123 & 0.101           & 0.114           & 0.235           \\
                                                            & (0.216)  & (0.234)         & (0.229)         & (0.232)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        Observations                                        & 9,232    & 9,824           & 10,423          & 10,076          \\
        Number sectors                                      & X        & 92              & 104             & 98              \\
        R$^{2}$                                             & 0.888    & 0.865           & 0.869           & 0.862           \\
        \bottomrule
        \\ %%% Create second table
        \multicolumn{1}{l}{\textbf{Panel B: SOE dominating sector}} \\
        \toprule
        & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\
        \cline{2-5}
        \\[-1.8ex] & (1) & (2) & (3) & (4)\\
        \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
        \hline \\[-1.8ex]
        TCZ_c \times \text{Polluted}_i \times \text{Period} & $-$0.138 & $-$0.243$^{**}$ & $-$0.272$^{**}$ & $-$0.284$^{**}$ \\
                                                            & (0.145)  & (0.124)         & (0.124)         & (0.125)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        Observations                                        & 21,444   & 20,852          & 20,253          & 20,600          \\
        Number sectors                                      & X        & 204             & 192             & 198             \\
        R$^{2}$                                             & 0.849    & 0.857           & 0.853           & 0.858           \\
      \end{tabular}
      \begin{tablenotes}
        \small
        \item Panel A
        Panel B \\
        Sources: Author's own computation
      \end{tablenotes}
    \end{threeparttable}
  }
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Dec 08, 2019 - 08:56:15
\begin{table}[!htbp] \centering
  \caption{SOE dominating sectors}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{cit}} \\
      \cline{2-5}
      \\[-1.8ex] & (1) & (2) & (3) & (4)\\
      \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
      \hline \\[-1.8ex]
      TCZ_c \times \text{Polluted}_i \times \text{Period} & $-$0.138 & $-$0.243$^{**}$ & $-$0.272$^{**}$ & $-$0.284$^{**}$ \\
                                                          & (0.145)  & (0.124)         & (0.124)         & (0.125)         \\
      \hline \\[-1.8ex]
      City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
      Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
      City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
      Observations                                        & 21,444   & 20,852          & 20,253          & 20,600          \\
      R$^{2}$                                             & 0.849    & 0.857           & 0.853           & 0.858           \\
      \hline
      \hline \\[-1.8ex]
      \textit{Note:}  & \multicolumn{4}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
      & \multicolumn{4}{l}{Heteroskedasticity-robust standard errors in parentheses} \\
      & \multicolumn{4}{l}{are clustered by city} \\
    \end{tabular}
  \end{adjustbox}
\end{table}

>>>>

\begin{table}[!htbp] \centering
  %\resizebox{1\textwidth}{!}{
    %\begin{threeparttable}
    \caption{SOE}
      \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
     \label{}
      \begin{tabular}{lrrrr}
        \multicolumn{1}{l}{\textbf{Panel A: SOE Dominating sector}} \\
        \toprule
        & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{ikt}} \\
        \cline{2-5}
        \\[-1.8ex] & (1) & (2) & (3) & (4)\\
        \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
        \hline \\[-1.8ex]
        TCZ_i \times \text{Polluted}_k \times \text{Period} & $-$0.123 & 0.101           & 0.114           & 0.235           \\
                                                            & (0.216)  & (0.234)         & (0.229)         & (0.232)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        Observations                                        & 9,232    & 9,824           & 10,423          & 10,076          \\
        Number sectors                                      & X        & 92              & 104             & 98              \\
        R$^{2}$                                             & 0.888    & 0.865           & 0.869           & 0.862           \\
        \bottomrule
        \\ %%% Create second table
        \multicolumn{1}{l}{\textbf{Panel B: Prviate Dominating sectors}} \\
        \toprule
        & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{ikt}} \\
        \cline{2-5}
        \\[-1.8ex] & (1) & (2) & (3) & (4)\\
        \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
        \hline \\[-1.8ex]
        TCZ_i \times \text{Polluted}_k \times \text{Period} & $-$0.138 & $-$0.243$^{**}$ & $-$0.272$^{**}$ & $-$0.284$^{**}$ \\
                                                            & (0.145)  & (0.124)         & (0.124)         & (0.125)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        Observations                                        & 21,444   & 20,852          & 20,253          & 20,600          \\
        Number sectors                                      & X        & 204             & 192             & 198             \\
        R$^{2}$                                             & 0.849    & 0.857           & 0.853           & 0.858           \\
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
      \\
    \end{tablenotes}
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Dec 08, 2019 - 08:56:15
\begin{table}[!htbp] \centering
  \caption{SOE dominating sectors}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{ikt}} \\
      \cline{2-5}
      \\[-1.8ex] & (1) & (2) & (3) & (4)\\
      \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
      \hline \\[-1.8ex]
      TCZ_i \times \text{Polluted}_k \times \text{Period} & $-$0.138 & $-$0.243$^{**}$ & $-$0.272$^{**}$ & $-$0.284$^{**}$ \\
                                                          & (0.145)  & (0.124)         & (0.124)         & (0.125)         \\
      \hline \\[-1.8ex]
      City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
      Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
      City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
      Observations                                        & 21,444   & 20,852          & 20,253          & 20,600          \\
      R$^{2}$                                             & 0.849    & 0.857           & 0.853           & 0.858           \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

### 2020-01-19 Temp_tables/table_7.tex
intend tables
update latex table

\begin{document}
% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sun, Dec 08, 2019 - 08:56:21
\begin{table}[!htbp] \centering 
  \caption{11th FYP city pollution reduction mandate} 
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{The Dependent variable: Ln SO2_{cit}} \\ 
\cline{2-3} 
\\[-1.8ex] & (1) & (2)\\ 
\\[-1.8ex] & (TCZ) & (No TCZ)\\
\hline \\[-1.8ex] 
   \text{Period} \times target_c \times \text{Polluted}_i  & $-$0.413$^{***}$ & $-$1.415 \\ 
  & (0.141) & (1.672) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes \\ 
Observations & 23,333 & 7,343 \\ 
R$^{2}$ & 0.847 & 0.892 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{2}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{2}{l}{are clustered by city} \\ 
\end{tabular} 
\end{adjustbox}
\end{table}

>>>>

\begin{document}

\begin{table}[!htbp] \centering
  \caption{11th FYP city pollution reduction mandate}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{2}{c}{The Dependent variable: Ln SO2_{ikt}} \\
      \cline{2-3}
      \\[-1.8ex] & (1) & (2)\\
      \\[-1.8ex] & (TCZ) & (No TCZ)\\
      \hline \\[-1.8ex]
      \text{Period} \times target_i \times \text{Polluted}_k & $-$0.413$^{***}$ & $-$1.415 \\
                                                             & (0.141)          & (1.672)  \\
      \hline \\[-1.8ex]
      City-year fixed effects                                & Yes              & Yes      \\
      Industry-year fixed effects                            & Yes              & Yes      \\
      City-industry fixed effects                            & Yes              & Yes      \\
      Observations                                           & 23,333           & 7,343    \\
      R$^{2}$                                                & 0.847            & 0.892    \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}
